Clinical prediction with localized modeling using similarity-based cohorts: A scoping review

### 2023-08-29 docs/Manuscript/Manuscript.Rmd
draft results subsection on identified needs for future work

>>>>

## Identified needs

The study authors focused their recommendations and their own plans for future work mostly on technical improvements and evaluations [@Mariuzzi1997; @Yearwood1997a].
Urged improvements included full or partial automation of user-dependent steps such as predictor selection [@Mariuzzi1997; @Yearwood1997a], similarity learning [@Mariuzzi1997; @Wang2019], and parameter optimization [@Song2006c; @Lee2017]; extensions to new data structures [@Lopez2011a], data types [@Liang2015a; @Verma2015a; @Malykh2018a], and reasoning systems [@Nicolas2014a]; and the use of more advanced model components to improve accuracy or efficiency [@Lowsky2013; @Lee2015; @Liang2015a; @Zhang2018a].
Authors also urged validations and independent evaluations using larger or more comprehensive data sets [@Elter2007a; @Xu2008a; @Verma2015a; @Ng2015], using data aggregated from multiple health systems [@Lee2015; @Lee2017; @Tang2021c; @Ng2021b], and in other care settings or disease contexts [@Song2006c; @Zhang2018a; @Tang2021c; @Ng2021b].
Less common were calls to strengthen the connection between the methods and the users.
Some authors urged the incorporation of (human-derived) domain knowledge into the data or models [@Yearwood1997a; @Wang2019]. Others suggested new uses of their modeling approaches: to measure feature importance [@Wyns2004a], to make models more expressive [@Lee2015], and to combine information obtained both from global and from localized models [@Ng2015].
Most of this incremental work was indeed carried out by later researchers whose output appears in our sample.

### 2023-08-29 docs/Manuscript/Manuscript.tex
draft results subsection on identified needs for future work

>>>>

\hypertarget{identified-needs}{%
\subsection{Identified needs}\label{identified-needs}}

The study authors focused their recommendations and their own plans for
future work mostly on technical improvements and evaluations
{[}11,19{]}. Urged improvements included full or partial automation of
user-dependent steps such as predictor selection {[}11,19{]}, similarity
learning {[}11,17{]}, and parameter optimization {[}16,21{]}; extensions
to new data structures {[}24{]}, data types {[}25,26,31{]}, and
reasoning systems {[}28{]}; and the use of more advanced model
components to improve accuracy or efficiency {[}12,14,26,30{]}. Authors
also urged validations and independent evaluations using larger or more
comprehensive data sets {[}15,22,23,25{]}, using data aggregated from
multiple health systems {[}14,16,34,35{]}, and in other care settings or
disease contexts {[}21,30,34,35{]}. Less common were calls to strengthen
the connection between the methods and the users. Some authors urged the
incorporation of (human-derived) domain knowledge into the data or
models {[}17,19{]}. Others suggested new uses of their modeling
approaches: to measure feature importance {[}20{]}, to make models more
expressive {[}14{]}, and to combine information obtained both from
global and from localized models {[}15{]}. Most of this incremental work
was indeed carried out by later researchers whose output appears in our
sample.
